\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-14 paper/main.tex
another pass

\section{Conclusion and Future Work}
Deep Learning (DL) Libraries (e.g., \torch) provide the basic blocks
for creating AI-enabled applications, which are becoming very
popular. Several testing techniques have been proposed in the
literature to find bugs on these libraries. Unfortunately, the lack of
a dataset of reproducible bugs in those libraries poses a barrier to
a proper evaluation of these techniques. \tname{} fills the gaps by

>>>>

\section{Conclusion and Future Work}
Deep Learning (DL) Libraries (e.g., \torch) provide the basic blocks
for creating AI-enabled applications, which are becoming very
popular. Several testing techniques have been proposed in the
literature to find bugs in these libraries. Unfortunately, the lack of
a dataset of reproducible bugs in those libraries poses an important
barrier to the proper evaluation of these techniques. \tname{} fills
the gaps. It includes a total of \numbugs\ across three major DL
libraries. We plan to continue expanding this dataset and to explore
automated approaches to extract patches from issue trackers and
``frontport'' them~\cite{hazimeh2020magma} to a single version of the
library to facilitate testing.
